===========================================================================================

JB_INSTAL_MXNET.Rmd

mxnet_0.10.1

For more documents, please visit http://mxnet.io

E:\MIJN DATA SCIENCE\_MIJN DATA SCIENCE PROJECTS\_R\GAN\GAN_EXAMPLE_R\gan_example-master

Creation Date: 16-10-2017
Last Edited  : 16-10-2017

Installing MXNET (MXNet: A Flexible and Efficient Machine Learning Library for Heterogeneous Distributed Systems)

https://mxnet.incubator.apache.org/get_started/install.html


Installing MXNet¶

Indicate your preferred configuration. Then, follow the customized commands to install MXNet.

1) Windows, R, CPU

The CPU version of MXNet R package can be installed in R like other packages

cran <- getOption("repos")
cran["dmlc"] <- "https://s3-us-west-2.amazonaws.com/apache-mxnet/R/CRAN/"
options(repos = cran)
install.packages("mxnet")

===========================================================================================


```{r}
cran <- getOption("repos")
cran["dmlc"] <- "https://s3-us-west-2.amazonaws.com/apache-mxnet/R/CRAN/"
options(repos = cran)
install.packages("mxnet") #MXNet: A Flexible and Efficient Machine Learning Library for Heterogeneous Distributed Systems
```



Validate MXNet Installation

Run a short MXNet R program to create a 2X3 matrix of ones a on a GPU, multiply each element in the matrix by 2 followed by adding 1. We expect the output to be a 2X3 matrix with all elements being 3. We use mx.gpu(), to set MXNet context to be GPUs.

library(mxnet)
a <- mx.nd.ones(c(2,3), ctx = mx.gpu())
b <- a * 2 + 1
b


```{r}
library(mxnet)  # For more documents, please visit http://mxnet.io
#a <- mx.nd.ones(c(2,3), ctx = mx.gpu())
a <- mx.nd.ones(c(2,3), ctx = mx.cpu())
b <- a * 2 + 1
b
```

===========================================================================================

```{r}
demo(package = "mxnet")
```

Demos in package ‘mxnet’:

basic_bench                Basic benchmark
basic_executor             Basic executor operations
basic_kvstore              Basic kvstore operations
basic_model                Basic model operations
basic_ndarray              Basic ndarray operations
basic_random               Basic random number generators
basic_symbol               Basic symbol operations


```{r}
demo(basic_bench, package = "mxnet")
```


```{r}
demo(basic_executor, package = "mxnet")
```



```{r}
demo(basic_kvstore, package = "mxnet")
```



```{r}
demo(basic_model, package = "mxnet")
```

```{r}
ls()
dir()
dir("C:/Users/Rinus/AppData/Local/Temp/Rtmpiwd8Me")
```





```{r}
demo(basic_ndarray, package = "mxnet")
```




```{r}
demo(basic_random, package = "mxnet")
```




```{r}
demo(basic_symbol, package = "mxnet")
```



===========================================================================================
===========================================================================================
